---
title: "Applied Statistical Methods Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Applied Statistical Methods Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL224753youn0052)
```

# Introduction

## myboot2.R and mybootadjusted.R

myboot2.R is a simple bootstrapping function for samples with statistical alpha. Includes several functionalities like "mean", "median", and so on, but can also take in user-defined functions. 

mybootadjusted.R is identical but returns a list of important variables as opposed to a plot.


Use cases:

```{r}
set.seed(39)

mean_over_median = function(x) {
  mean_over_median = mean(x) / median(x)
}
sam = rnorm(25, mean = 25, sd = 10)

myboot2(x = sam, fun = mean_over_median)


sam = c(1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 4, 4)

data = mybootadjusted(x = sam, fun = "median")
factored = table(factor(data[4]$xstat, levels = c(1:4)))

barplot(factored, xlab = "xstat", col = 3)
```


## myncurve.R

Given $\mu$, $a$, and $\sigma$, plots a dnorm function as well as the probability of $P(Y\leq a)$.

Use case:

```{r}
myncurve(mu = 10, sigma = 5, a = 6)
```

## ntickets.R

Solves the overbooking problem by calculating the optimal number of tickets to be sold, both discretely, and with a normal approximation to the binomial distribution.

Use case:

```{r}
ntickets(N = 400, gamma = 0.02, p = 0.95)
```

## hypergeom.R

Computes the an approximation of the probability mass function of the hyper geometric distribution.

Use case:

```{r}
hypergeom(iterations = 10, num_trials = 5, total_y = 12, total_obj_num = 20)
```
